Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-04-03 overall.tex
Address Jack's issue #13

Investigations showed an average CPU load of 3.6\% on the upgraded DTNs. As
such, further hardware upgrades seem unlikely to improve significantly the
performance of PanDA Brokers. Nonetheless, current DTN load suggests that the
number of brokers per DTN could be further increased. This would enable the
submission of a larger number of concurrent jobs to Titan's PBS queue, allowing
for PanDA to consume a higher percentage of backfill availability.

It should be noted that increasing the number of brokers requires also to
increase the number of concurrent jobs that can be submitted to Titan's queue.
Each broker submits 1 job at a time with at least 2 hours walltime. Backfill
availability is polled every 10 minutes, giving a theoretical maximum of 110
concurrent jobs submitted to Titan. Titan's policy was already changed in
September 2016, enabling the submission of 20 concurrent jobs and the deployment
of 20 PanDA brokers. Further study is required to understand the impact that a
larger amount of concurrent queued jobs would have on the overall efficiency of
Titan's scheduler.

>>>>

Investigations showed an average CPU load of 3.6\% on the upgraded DTNs. As
such, further hardware upgrades seem unlikely to improve significantly the
performance of PanDA Brokers. Nonetheless, current DTN load suggests that the
number of brokers per DTN could be increased. In September 2016, increasing the
number of concurrent PanDA Broker from 4 to 20 markedly improved efficiency (see
Fig.~\ref{fig:backfill-utilization}) but further research is needed to
understand whether an even larger number brokers would allow PanDA to consume a
higher percentage of backfill availability.
